Occultation Light Curves in Reflected Light

### 2020-03-30 tex/ms.tex
added fig

% Title
\title{Analytic Light Curves in Reflected Light}

@@

%
\section{Introduction}
%
This is an extension of \citep{Luger2019}.

@@

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight families of cases of occultations in reflected light.
            In these figures, the night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted). The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the red boundary (the curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
            \S\ref{sec:integration}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/geometry.pdf}
        \oscaption{geometry}{%
            Geometry of an occultation in reflected light, corresponding
            to case 5 in Figure~\ref{fig:cases}. The surface integral over
            the blue region is computed from the antiderivatives of the
            surface intensity map counter-clockwise along the boundary curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
            \label{fig:geometry}
        }
    \end{centering}
\end{figure}

As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
are given by the line integral
%
\begin{align}
    \label{eq:s}
    \mathbf{s}_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
\end{align}
%
where
%
\begin{align}
    \label{eq:G}
    \bvec{G}_{\mu,\nu} (x, y) & =
    \begin{dcases}
        %
        x^{\frac{\mu + 2}{2}}
        y^{\frac{\nu}{2}}
        \,\yhat
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x^{l-2}
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        x^{l-3}
        y
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{odd}
        \\[1em]
        %
        x^{\frac{\mu-3}{2}}
        y^{\frac{\nu-1}{2}}
        z(x, y)^3
        \,\yhat
         & \qquad \mathrm{otherwise,}
    \end{dcases}
\end{align}
%
and
%
\begin{align}
    \dd \bvec{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
    r \cos\varphi \, \dd \varphi \, \yhat
    \quad,
\end{align}
%
where $\varphi = \varphi(x, y)$ is the parametrized angle along the
arc of integration. Generally, there are at most three arcs bounding a given
closed surface of integration, which we will denote $\mathcal{P}$,
$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical occultor-occulted
configuration in Figure~\ref{fig:geometry}.

>>>>

% Title
\title{Occultation Light Curves in Reflected Light}

@@

%
\section{Introduction}
\label{sec:intro}
%
This is an extension of \citet{Luger2019}.

\pagebreak

%
\section{The Problem}
\label{sec:the-problem}

As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
a spherical body whose surface intensity is described by the spherical harmonic
coefficient vector $\mathbf{y}$ as
%
\begin{align}
    \label{eq:sTARRy}
    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
    \quad,
\end{align}
%
where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices,
$\bvec{A}$ is a change-of-basis matrix to a basis $\tilde{\bvec{g}}$,
and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
of the basis functions in $\tilde{\bvec{g}}$ over
the projected visible disk of the body (which may be partially occulted by
another spherical body).
For more information on these terms, the reader is referred to
\citet{Luger2019}.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.35\linewidth]{figures/illum.pdf}
        \oscaption{illum}{%
            Illumination geometry.
            \label{fig:illum}
        }
    \end{centering}
\end{figure}

The derivations in \citet{Luger2019} assume that the coefficient vector
$\mathbf{y}$ describes the \emph{emissivity} of the body, which (in the
absence of limb darkening) is assumed to be Lambertian, i.e., all points on the
surface emit equally in all directions.
Here, we derive the solution to the occultation problem for Lambertian
reflectance, in which case the vector $\mathbf{y}$ describes the
surface \emph{reflectivity} (or \emph{Bond albedo}). Specifically, we assume
the body is illuminated by a point-like source and the radiance at any point
is proportional to the cosine of the angle between the incident light
and the surface normal. Points for which this angle is greater than
$\frac{\pi}{2}$ are unilluminated and therefore have radiance of zero;
see Figure~\ref{fig:illum}.

% case 1: 0
% case 2: sTr
% case 3: sTe * I + ~sTr
% case 4: sTe * I
% case 5: sTr - sT0 * I
% case 6: (sTe + sT0) * I + ~sTr
% case 7: (sTe - sT0) * I
% case 8: sT0 * I

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight families of cases of occultations in reflected light.
            In these figures, the night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted). The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the red boundary (the curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$ of
            \S\ref{sec:integration}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

\section{Cases 1--4}
\label{sec:cases-1-4}
TODO.

\section{Cases 5--8}
\label{sec:cases-5-8}

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/geometry.pdf}
        \oscaption{geometry}{%
            Geometry of an occultation in reflected light, corresponding
            to case 5 in Figure~\ref{fig:cases}. The surface integral over
            the blue region is computed from the antiderivatives of the
            surface intensity map counter-clockwise along the boundary curves
            $\mathcal{P}$, $\mathcal{T}$, and $\mathcal{Q}$.
            \label{fig:geometry}
        }
    \end{centering}
\end{figure}

As in \citet{Luger2019}, the elements of the solution vector $\mathbf{s}^\top$
are given by the line integral
%
\begin{align}
    \label{eq:s}
    s_{n(\mu,\nu)} = \oint \mathbf{G}_{\mu,\nu} \cdot \dd\mathbf{r}
\end{align}
%
where
%
\begin{align}
    \label{eq:G}
    \bvec{G}_{\mu,\nu} (x, y) & =
    \begin{dcases}
        %
        x^{\frac{\mu + 2}{2}}
        y^{\frac{\nu}{2}}
        \,\yhat
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        \frac{1-z(x, y)^3}{3(1-z(x, y)^2)}\bigg(-y \, \xhat + x \, \yhat\bigg)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        x^{l-2}
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        x^{l-3}
        y
        z(x, y)^3
        \,\xhat
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{odd}
        \\[1em]
        %
        x^{\frac{\mu-3}{2}}
        y^{\frac{\nu-1}{2}}
        z(x, y)^3
        \,\yhat
         & \qquad \mathrm{otherwise,}
    \end{dcases}
\end{align}
%
and
%
\begin{align}
    \dd \bvec{r} & = -r \sin\varphi \, \dd \varphi \, \xhat +
    r \cos\varphi \, \dd \varphi \, \yhat
    \quad,
\end{align}
%
where $\varphi = \varphi(x, y)$ is the parametrized angle along the
arc of integration. Generally, there are at most three arcs bounding a given
closed surface of integration, which we will denote $\mathcal{P}$,
$\mathcal{Q}$, and $\mathcal{T}$. These are shown for a typical occultor-occulted
configuration in Figure~\ref{fig:geometry}.

\section{Performance}
\label{sec:performance}

@@
